Merging Datasets Through Deep learning

### 2018-09-04 paper2018/evaluation.tex
wording
stuff

We report multiple metrics to measure the effectiveness of training, some of which are not standard because of the experimental setup, so we define them below:
\begin{itemize}
\item \textbf{Recall}.  Recall is measured by the percentage of positives in the nearest neighbor set of each anchor.
\item \textbf{Precision@1}.  Precision@1 is measured by the percentage of anchors with the very nearest neighbor being a positive.  As pointed out earlier, this is an important metric for assessing join performance in a majority of cases.
\item \textbf{Precision}.  Precision is measured by the percentage of all positives for each anchor that were closer to the anchor than any other negative relative to the size of the positive set.
\end{itemize}

@@

\subsection{Generalization Test on Faces}
We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.  To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:conf/cvpr/SchroffKP15}.  We took the two open sourced models \footnote{\url{https://github.com/davidsandberg/facenet}}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.  We put these output embeddings into an ANN structure, and computed our metrics on that.  Note that for face datasets there is a greater number of variability of faces per identity with a maximum of 529 faces for a single identity.  We adjusted neighborhood length to a maximum of 20 or the number of expected neighbors in our experiments for each face.  Recall was 91\% on the VGGFace2 dataset, and 87\% for the Casia Web Face dataset.  Precision@1 was 95\% for VGGFace2 and 93\% for Casia Web faces.  Overall precision was 91\% for VGGFace2 and Casia Web faces was 87\%.  These results suggest that existing models can in fact be re-purposed for joins.  We point out that the face models seem better in terms of performance compared to our model for names but there are significant differences in the data characteristics for training.  The names data had a lot fewer positives per identity (mostly 2.2 for companies, and 4.69 for people).  VGGFace2 has 362.6 faces per identity, and 500,000 images for 10,000 identities in CasiaWebFace.

>>>>

We report multiple metrics to measure the effectiveness of training, some of which are not standard because of the experimental setup, so we define them below:
\begin{itemize}
\item \textbf{Recall}.  Recall is measured by the percentage of positives in the nearest neighbor set of each anchor.
\item \textbf{Precision@1}.  Precision@1 is measured by the percentage of anchors with the very nearest neighbor being a positive.  As pointed out earlier, this is an important metric for assessing join performance in a majority of cases.
\item \textbf{Precision}.  Precision is measured by the fractions of all positives for each anchor that were closer to that anchor than was any negative.
\end{itemize}

@@

\subsection{Generalization Test on Faces}
We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.  To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:conf/cvpr/SchroffKP15}.  We took the two open sourced models \footnote{\url{https://github.com/davidsandberg/facenet}}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.  We put these output embeddings into an ANN structure, and computed our metrics on that.  Note that for face datasets there is a greater number of variability of faces per identity with a maximum of 529 faces for a single identity.  We adjusted neighborhood length to a maximum of 20 or the number of expected neighbors in our experiments for each face.  Recall was 91\% on the VGGFace2 dataset, and 87\% for the Casia Web Face dataset.  Precision@1 was 95\% for VGGFace2 and 93\% for Casia Web faces.  Overall precision was 91\% for VGGFace2 and Casia Web faces was 87\%.  These results suggest that existing models can in fact be re-purposed for joins.  We point out that the face models seem better in terms of performance compared to our model for names but there are significant differences in the data characteristics for training.  The names data had a lot fewer positives per identity.  VGGFace2 has 362.6 faces per identity, and 500,000 images for 10,000 identities in CasiaWebFace.

### 2018-09-04 paper2018/relatedWork.tex
stuff

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.   Since we do not use batches in triplet selection, but rather neighborhoods, our loss function also operates with a global perspective.

>>>>

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{DBLP:conf/cvpr/SongXJS16}, \cite{songCVPR17}.   Since we do not use batches in triplet selection, but rather neighborhoods, our loss function also operates with a global perspective.

### 2018-09-04 paper2018/triplet_selection.tex
stuff

\subsection{Metric Based Triplet Selection}
For the problem of joins, we ideally want the anchor and all of its positives to be clustered closest together and separated from the nearest negatives as clearly as possible.  Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.  They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.  The average complexity to query the vectors of a neighbor is $O(log N)$ where N is the number of vectors in the dataset.  Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.  In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.

>>>>

\subsection{Metric Based Triplet Selection}
For the problem of joins, we ideally want the anchor and all of its positives to be clustered closest together and separated from the nearest negatives as clearly as possible.  Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.  They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.  The average complexity to query the vectors of a neighbor is $O(log N)$ where N is the number of vectors in the dataset.  Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.  In our work, we used the Annoy ANN implementation \footnote{\url{https://github.com/spotify/annoy}} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.
